### 2024-02-05 README.Rmd
alter tabs

```{r}
st_bridges(df = df_scaled_sf|> filter(region %in% c("Wales","South West")),
           geom_col_name = "constituency_name",
           link_islands_k = 2
)  |> 
  st_manual_join_nb("Gower","St Ives")
```

>>>>

```{r}
st_bridges(df = df_scaled_sf|> filter(region %in% c("Wales","South West")),
           geom_col_name = "constituency_name",
           link_islands_k = 2)  |> 
  st_manual_join_nb("Gower","St Ives")
```
